---
title: "Home"
site: workflowr::wflow_site
output:
    workflowr::wflow_html:
      toc: false
      editor_options:
    chunk_output_type: console
---

<<<<<<< HEAD
```{r data_prep}
=======

```{r data_prep, include=FALSE}
>>>>>>> fbf4c652887e6bea159c644d8e2799f17c19660c
source('_drake.R')

con <- RPostgreSQL::dbConnect(DBI::dbDriver("PostgreSQL"),
                              user="dewoller", password=db_password,
                              host="alf", port=5432, dbname="postgis_db")

oneGraphSet = function (buffer_size) {

  cat(glue::glue('# Graphs for {buffer_size} M buffer</h2>'))
  dbGetQuery(con, glue::glue("
             with mb_cities as (
                                select mb_code16, gcc_name16
                                from meshblock
                                where gcc_code16 like '_G%' or gcc_code16 = '8ACTE'
             )
             select mb.mb_code16, gcc_name16, mb.mb_category_name_2016, population_covered, intersection_area, category_proportion
             from
             meshblock_statistics_{buffer_size} mb
             join meshblock_detail md using (mb_code16)
             join mb_cities mc using (mb_code16)
             where md.mb_category_name_2016 ='Residential'
             ")) %>%
             as_tibble() %>%
             { . } -> df_stats

  df_stats %>%
    ggplot( aes( y=intersection_area, x=gcc_name16, fill=gcc_name16 )) +
    geom_violin() +
    facet_wrap( ~mb_category_name_2016, scales='free', ncol=1) +
    coord_flip() +
    ggtitle( "Neighbourhood Category Areas (in m^2) around all Residential Meshblocks"   ) %>%
    { . } -> p
  print(p)

  df_stats %>%
    filter(mb_category_name_2016 %in% c('Residential','Commercial','Parkland')) %>%
    ggplot( aes( y=category_proportion, x=gcc_name16, fill=gcc_name16 )) +
    geom_violin() +
    facet_wrap( ~mb_category_name_2016, scales='free', ncol=1) +
    coord_flip() +
    ggtitle( "Neighbourhood Category Proportion for Residential, Commerical and Parklands around all Residential Meshblocks"   ) %>%
    { . } -> p
  print(p)
}




```

#  Graphs

```{r graphs, echo=FALSE, fig.height=15, fig.width=10}
oneGraphSet(5000)
oneGraphSet(2000)
oneGraphSet(1000)
oneGraphSet(400)

```


Sq km for each category, for each distance, for each
source_category = residential

output
source_MB, land_use_target_category, distance_category,
sa4 category, sqkm of category, proportion of all categories


parklands, commercial, land use mix

Walkability - commercial, parklands, residential

street connections


