---
title: "Home"
site: workflowr::wflow_site
output:
    workflowr::wflow_html:
      toc: false
---


  ```{r "setup", include=FALSE}
knitr::opts_knit$set(root.dir = '..')  # with something else than `getwd()`
```


# compare R calculated neighbourhoods with SQL calculated neighbourhood

We recalculated a 1% random sample of meshblock neighbourhoods using the R sf package (n=3581), for each of the four neighbourhood distance threshholds.  We reused the centroids calculated by postgis, because it is a weighted geographic centroid that is not the same as the centroid returned by the sf package. The R calculated neighbourhoods were broad similar to those calculated by postGIS, with all parameters within .05% of each other.  The reason for the difference are as follows:

- differences in the methods of transformation between spatial reference systems
- differences in the way the buffer around the centroid is calculated (e.g. the number of segments in the circle around the centroid)


Postgis has about 0.58% larger area calculations than R.



```{r data_prep, include=FALSE}
browser()
source('_drake.R')

print('here')

  c(400,1000,2000, 5000) %>%
  enframe(name=NULL, value='distance') %>%
  mutate( area_max = distance ^2 * pi) %>%
  { . } -> distance_theoretical_totals

loadd(df_mesh_centroids_sample )

bind_rows(
          readd(df_mesh_within_range_400) ,
          readd(df_mesh_within_range_1000),
          readd(df_mesh_within_range_2000),
          readd(df_mesh_within_range_5000)
          ) %>%
mutate( intersection_area = as.numeric( intersection_area)) %>%
{ . } -> df_mesh_within_range_area

print('here')

df_mesh_centroids_sample  %>%
  anti_join( df_mesh_within_range_area)

   df_mesh_within_range_area %>%
   count( mb_code16, distance)
 print('here')

df_mesh_within_range_area %>%
  group_by(mb_code16, mb_cat16.1, distance) %>%
  summarise(
            intersection_area=sum(intersection_area),
            .groups='drop'
  ) %>%
  rename( mb_category_name_2016=mb_cat16.1 ) %>%
  { . } -> df_c_r

print('here')


df_c_r %>%
  group_by( mb_code16, distance) %>%
  summarise( intersection_area = sum( intersection_area), .groups='drop') %>%
  { . } -> df_c_r_total

print('here')

```

# Load in postgis calculated data

```{r load_postgis}

################################################################################yy#####

  con <- RPostgreSQL::dbConnect(DBI::dbDriver("PostgreSQL"),
                                user="dewoller", password=db_password,
                                host="localhost", port=5432, dbname="postgis_db")

dbGetQuery(con, "
           ---
             select mb.mb_code16, distance, mb.to_mb_code16, intersection_area, proportion_covered
           from meshblock_concordance mb
           join meshblock_detail md using (mb_code16)
           join df_mesh_centroids_sample sample using (mb_code16)
           ---
             " ) %>%
           as_tibble() %>%
           { . } -> df_concordance_sql

  dbGetQuery(con, "
             ---
select mb.mb_code16, distance, mb.mb_category_name_2016, population_covered, intersection_area, category_proportion
from meshblock_statistics mb
join meshblock_detail md using (mb_code16)
join df_mesh_centroids_sample sample using (mb_code16)
---
" ) %>%
as_tibble() %>%
{ . } -> df_c_sql

df_c_sql %>%
  group_by( mb_code16, distance) %>%
  summarise( intersection_area = sum( intersection_area), .groups='drop') %>%
  { . } -> df_c_sql_total
################################################################################yy#####


```

# analysis - comparison at category level
 - difference is the R calculated amount - SQL calculated amount at land use level
```{r}

################################################################################yy#####


df_c_sql  %>%
  full_join( df_c_r, by=c( 'mb_code16', 'mb_category_name_2016', 'distance' ), suffix=c('.c_r','.c_sql')) %>%
mutate( diff= intersection_area.c_r - intersection_area.c_sql,
       pct = diff / intersection_area.c_sql) %>%
arrange( desc( diff)) %>%
arrange( desc( pct)) %>%
{ . } -> df_diff

df_diff %>%
  drop_na() %>%
  summarise( across( where(is.numeric), .fns=c('mean'=mean, 'median'=median)))


df_diff %>%
ggplot( aes( diff)) + geom_histogram()

df_diff %>%
  ggplot( aes( diff)) + geom_histogram() +
  facet_wrap(~distance, scale='free')


df_diff %>%
  ggplot( aes( intersection_area.c_sql, intersection_area.c_r, color=as.factor(distance))) +
  geom_point()

```

# grand total area coverage
- note that R calculated total is consistently less than the SQL calculated total
```{r }

df_c_sql_total  %>%
  full_join( df_c_r_total, by=c( 'mb_code16', 'distance'), suffix=c('.c_r','.c_sql')) %>%
  inner_join( distance_theoretical_totals, by='distance') %>%
  mutate( diff= as.numeric(intersection_area.c_sql) - intersection_area.c_r ) %>%
  mutate( diff_from_max.c_r = area_max -   intersection_area.c_r) %>%
  mutate( diff_from_max.c_sql = area_max -   intersection_area.c_sql) %>%
  arrange( desc( diff)) %>%
  { . } -> df_diff_total

df_diff_total %>%
  ggplot( aes( diff)) + geom_histogram() +
facet_wrap(~distance, scale='free')

df_diff_total %>%
  ggplot( aes( diff_from_max.c_sql)) + geom_histogram() +
  facet_wrap(~distance, scale='free')

df_diff_total %>%
  ggplot( aes( diff_from_max.c_r)) + geom_histogram() +
  facet_wrap(~distance, scale='free')

df_diff_total %>%
ggplot( aes( diff_from_max.c_r, diff_from_max.c_sql)) +
geom_point() +
  facet_wrap(~distance, scale='free')

df_diff_total %>%
  ggplot( aes( intersection_area.c_sql, intersection_area.c_r)) +
  geom_point() +
  facet_wrap(~distance, scale='free')

df_diff_total %>%
  ggplot( aes( intersection_area.c_sql, intersection_area.c_r, color=as.factor(distance))) +
  geom_point()

df_c_r_total %>%
  arrange( ( intersection_area)) %>%
  ggplot( aes( intersection_area)) + geom_histogram()


df_diff_total %>%
  summarise( across(where(is_numeric), .fns=sum) ) %>%
  gt()

df_diff_total %>%
  group_by(distance) %>%
  summarise( across(where(is_numeric), .fns=sum) )  %>%
  gt()


```



# compare individual concordances

```{r compare_concordances}

df_mesh_within_range_area %>%
  rename( to_mb_code16 = mb_code16.1) %>%
  inner_join( df_concordance_sql, by=c('mb_code16','to_mb_code16', 'distance'), suffix=c('.c_r','.c_sql')) %>%
  mutate( diff= intersection_area.c_r - intersection_area.c_sql,
         pct = diff / intersection_area.c_sql) %>%
  { . } -> df_both_concord


df_both_concord %>%
  drop_na() %>%
  filter( pct != Inf) %>%
  select(diff, pct) %>%
  summarise( across( where(is.numeric), .fns=c('mean'=mean, 'median'=median)))

df_both_concord %>%
drop_na() %>%
filter( pct != Inf) %>%
group_by(distance) %>%
select(diff, pct) %>%
summarise( across( where(is.numeric), .fns=c('mean'=mean, 'median'=median)))

```


# Compare Total Summary

```{r total_summary}

dbGetQuery(con, "
           ---
             select mb.mb_code16, distance, mb.mb_category_name_2016, population_covered, intersection_area, category_proportion
           from meshblock_statistics mb
           join meshblock_detail md using (mb_code16)
           ---
             " ) %>%
           as_tibble() %>%
           { . } -> df_c_sql_all

         df_c_sql_all %>%
           group_by( mb_code16, distance) %>%
           summarise( intersection_area = sum( intersection_area), .groups='drop') %>%
           { . } -> df_c_sql_total

         df_c_sql_total %>%
           mutate(distance=as.factor(distance)) %>%
           ggplot( aes( intersection_area, fill=distance)) +
           geom_histogram()  +
           facet_wrap(~distance, scale='free')

```
